Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-12-02 paper/main.tex
rework again

\begin{figure}[H]
    \centering
    \includestandalone[width=0.8\textwidth]{figures/concept/overview}
    \caption{
        The project can be divided into subcomponents that interact with and depend on
        each other.
        Every component implicitly builds on the spatial representation of rod-shaped bacteria as
        vertices (see \nameref{subsec:spatial-representation}).
        Red boxes highlight the key scientific drivers of this study while yellow boxes indicate
        auxiliary methods.
        The blue box "Data Generation" displays a extension of this approach which is under active
        development.
    }
    \label{fig:flowchart-project-structure}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includestandalone[width=0.8\textwidth]{figures/concept/overview}
    \caption{
        Modular framework for parameter estimation of elongated bacteria.
        The framework relies on a unified spatial representation (left) which discretizes
        bacteria into vertices.
        Building on top are visualization methods (top), a novel computational model for flexible
        elongated bacteria (middle) and data extraction routines (bottom).
        Analysis methods (bottom right) utilize extraction methods and can be informed by the model
        or used to guide modeling choices.
        The parameter estimation module integrates the preceding ones and allows us to calibrate the
        model which can then be used in generating synthetic data (top right).
        Colors indicate the component type; core scientific drivers (red), auxiliary methods (yellow)
        and extensions (blue).
    }
    \label{fig:flowchart-project-structure}
\end{figure}
